---
params: 
  title: "Calibration Certificate Information"
  author: "Calibrating Laboratory"
  address: "Adress"
  date: '`r format(Sys.Date(), "%B %d, %Y")`'
  NAWIDCC: na
  logoBolean: na
output: 
  pdf_document:
      keep_tex: true
geometry: left = 20mm, right = 20mm, top = 10mm, bottom = 45mm
header-includes:    
    \usepackage{fancyhdr, graphicx, eurosym, booktabs, xcolor, lastpage}
    \pagestyle{fancy}   
    \fancyhf{}
    \addtolength{\headheight}{2.5cm}
    \fancyheadoffset{10mm}
    \lhead{\IfFileExists{logo.png}{\includegraphics[height = 2cm]{logo.png}}}
    \lfoot{Page \thepage~of~\pageref{LastPage}}
    \fancypagestyle{plain}{\pagestyle{fancy}}
    \renewcommand{\headrulewidth}{0pt}
    \setlength{\headsep}{12mm}
    \usepackage{titling}
    \usepackage{booktabs}
    \usepackage{multicol}
    \usepackage{caption}
    \setlength{\belowcaptionskip}{0pt plus 1pt minus 1pt}
    \usepackage{hyperref}
    \hypersetup{urlcolor = cyan}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(masscor)
library(xtable)
library(knitr)

  NAWIDCC <- readRDS('../ExampleFiles/DCC_NAWI_Balanza Mettler Toledo XPE 205_B743848411 _ AF-07090_2020-07-16.rds')
 # NAWIDCC <- params$NAWIDCC
 LinkMasscor <- 'http://186.155.29.169:3838/masscor/'

 FRMT <- function(x) {format(x, scientific = FALSE, nsmall = abs(floor(log10(convertMassUnitsSI(NAWIDCC$d, from = NAWIDCC$standardUnits, to = NAWIDCC$orgRepUnits[1])))))}

```

$~$

\vspace{5ex}
\begin{center}\textsc{\huge Calibration Certificate Information}\end{center}
\vspace{8ex}\textbf{\Large `r gsub("(?<!\\w)(.)","\\U\\1", tolower(params$author), perl = TRUE)`}\newline
\textbf{`r params$address`}
\vspace{4ex}

## Certificate number: **`r NAWIDCC$add.info$CertificateNumber`**

$\hrulefill$

$~$

 \begin{tabular}{@{$\qquad\qquad$}rp{0.7\linewidth}}
 \textbf{\large Object to calibrate:}&\textbf{\large Non Automatic Weighing Instrument (NAWI)}\\[3ex]
 \textbf{Identification:}&`r NAWIDCC$balanceID`\\
 \textbf{Serial:}&`r NAWIDCC$serial`\\
 \textbf{Calibration date:}&`r NAWIDCC$date`\\
 \textbf{Calibration place:}&`r NAWIDCC$add.info$CalibrationPlace`\\[2ex]
 \textbf{Responsible person:}&`r strsplit(x = NAWIDCC$add.info$ResponsiblePerson, split = ',')[[1]][1]`\\
                     &`r ifelse(is.na(strsplit(x = NAWIDCC$add.info$ResponsiblePerson, split = ',')[[1]][2]), '', strsplit(x = NAWIDCC$add.info$ResponsiblePerson, split = ',')[[1]][2])`\\
                     &`r ifelse(is.na(strsplit(x = NAWIDCC$add.info$ResponsiblePerson, split = ',')[[1]][3]), '', strsplit(x = NAWIDCC$add.info$ResponsiblePerson, split = ',')[[1]][3])`\\[2ex]
\multicolumn{2}{@{}l}{\textit{Environmental conditions during calibration}}\\
\textbf{Ambient temperature:} & `r paste(NAWIDCC$Temp, ifelse(NAWIDCC$unitsENV[1] == 'deg.C', '$^oC$', NAWIDCC$unitsENV[1]), sep = ' ')`\\
\textbf{Barometric pressure:} & `r paste(NAWIDCC$p, NAWIDCC$unitsENV[2], sep = ' ')`\\
\textbf{Relative humidity:}   & `r paste(NAWIDCC$h, ifelse(NAWIDCC$unitsENV[3] == '%', '\\%', ''), sep = ' ')`\\
\end{tabular}

$~$

$\hrulefill$

\vspace{1ex}
## NAWI description

\begin{tabular}{@{$\qquad\qquad\qquad$}rrl}
 \textbf{ Maximum load:}&\textbf{`r max(NAWIDCC$indError[, 1])`} & `r NAWIDCC$orgdUnits`\\
 \textbf{ Minimum load:}&\textbf{`r min(NAWIDCC$indError[, 1])`} & `r NAWIDCC$orgdUnits`\\
 \textbf{ Readability:} &\textbf{`r convertMassUnitsSI(NAWIDCC$d, from = NAWIDCC$standardUnits, to = NAWIDCC$orgdUnits)`} & `r NAWIDCC$orgdUnits`\\
\end{tabular} 
   

$~$

$\hrulefill$

\begin{flushright}
  \texttt{masscor App Version: `r NAWIDCC$add.info$masscorAppVersion`}
  
  \texttt{\url{`r LinkMasscor`}}
\end{flushright}

\clearpage

## Repeatability test results

```{r, echo = FALSE}
kable(rbind(t(apply(NAWIDCC$add.info$CompleteRepeatability, MARGIN = 2, FRMT)), '.' = rep('', nrow(NAWIDCC$add.info$CompleteRepeatability)),
            Load = format(NAWIDCC$rep$V1, scientific = FALSE, digits = 4), 'Standard.deviation' = signif(NAWIDCC$rep$V2, 2)),
      format = "simple", caption = paste0('Repeatability test data. Units: [', NAWIDCC$orgRepUnits[1], ']'), align = 'r',
      col.names = paste(rownames(NAWIDCC$add.info$CompleteRepeatability), '/', NAWIDCC$orgRepUnits[1], sep = ' '), booktabs = TRUE)
```

$\hrulefill$

## Excentricity test results
\begin{minipage}{.3\textwidth}
  \includegraphics[width = 3cm]{eccen.png}
\end{minipage}
\begin{minipage}{.5\textwidth} 
    \captionof{table}{Eccentricity test results}
    \begin{tabular}{c r r}\toprule
    \textbf{Position} & \textbf{Indication / `r NAWIDCC$orgEccenUnits[1]`} & \textbf{Difference / `r NAWIDCC$orgEccenUnits[1]`}\\\midrule
    1 (Central position) & `r FRMT(NAWIDCC$add.info$CompleteEccentricity[[1]][1])` & -\\
    2 & `r FRMT(NAWIDCC$add.info$CompleteEccentricity[[1]][2])` & `r FRMT(NAWIDCC$add.info$CompleteEccentricity[[1]][2] - NAWIDCC$add.info$CompleteEccentricity[[1]][1])`\\
    3 & `r FRMT(NAWIDCC$add.info$CompleteEccentricity[[1]][3])` & `r FRMT(NAWIDCC$add.info$CompleteEccentricity[[1]][3] - NAWIDCC$add.info$CompleteEccentricity[[1]][1])`\\
    4 & `r FRMT(NAWIDCC$add.info$CompleteEccentricity[[1]][4])` & `r FRMT(NAWIDCC$add.info$CompleteEccentricity[[1]][4] - NAWIDCC$add.info$CompleteEccentricity[[1]][1])`\\
    5 & `r FRMT(NAWIDCC$add.info$CompleteEccentricity[[1]][5])` & `r FRMT(NAWIDCC$add.info$CompleteEccentricity[[1]][5] - NAWIDCC$add.info$CompleteEccentricity[[1]][1])`\\\midrule
    \multicolumn{2}{c}{\textbf{Maximum difference}}&`r FRMT(NAWIDCC$eccen[2])`\\\bottomrule
    \end{tabular}
\end{minipage}

$~$

$\hrulefill$

\clearpage
## Indication error test
```{r, echo = FALSE, out.width = "100%", fig.width = 10, fig.height = 3, fig.cap = "Indication error plot for the NAWI."}
  par(mar = c(4, 4, 0.1, 0.1))  
  plot(NAWIDCC, cex = 0.5)
```
```{r, echo = FALSE}
kable(cbind(Load = NAWIDCC$indError[, 1], 
            Error = format(convertMassUnitsSI(NAWIDCC$indError[, 2], from = NAWIDCC$standardUnits, to = NAWIDCC$orgIndErrorUnits[2]),
                           scientific = FALSE, nsmall = abs(floor(log10(convertMassUnitsSI(NAWIDCC$d, from = NAWIDCC$standardUnits, to = NAWIDCC$orgIndErrorUnits[2]))))),
            Uncertainty = format(convertMassUnitsSI(NAWIDCC$indError[, 3], from = NAWIDCC$standardUnits, to = NAWIDCC$orgIndErrorUnits[3]),
                           scientific = FALSE, nsmall = abs(floor(log10(convertMassUnitsSI(NAWIDCC$d, from = NAWIDCC$standardUnits, to = NAWIDCC$orgIndErrorUnits[3])))))),
      format = "simple", caption = 'Indication error test results', align = 'r',
      col.names = paste0(c('Load / ', 'Error / ', 'Uncertainty / '), NAWIDCC$orgIndErrorUnits), booktabs = TRUE)
```
Uncertainties correspond to `r ifelse(NAWIDCC$k == 1, 'standard', paste0('expanded'))`

$\hrulefill$

\clearpage

## Comments section
`r NAWIDCC$add.info$Comments$Com1`\vspace{2ex}

`r NAWIDCC$add.info$Comments$Com2`\vspace{3ex}

`r NAWIDCC$add.info$Comments$Com3`

`r NAWIDCC$add.info$Comments$Com4`