---
params: 
  title: "Calibration Certificate Information"
  author: "Calibrating Laboratory"
  address: "Adress"
  date: '`r format(Sys.Date(), "%B %d, %Y")`'
  NAWIDCC: na
  logoBolean: na
output: 
  pdf_document:
      keep_tex: true
geometry: left = 20mm, right = 20mm, top = 10mm, bottom = 45mm
header-includes:    
    \usepackage{fancyhdr, graphicx, eurosym, booktabs, xcolor, lastpage}
    \pagestyle{fancy}   
    \fancyhf{}
    \addtolength{\headheight}{2.5cm}
    \fancyheadoffset{10mm}
    \lhead{\IfFileExists{logo.png}{\includegraphics[height = 2cm]{logo.png}}}
    \lfoot{Page \thepage~of~\pageref{LastPage}}
    \fancypagestyle{plain}{\pagestyle{fancy}}
    \renewcommand{\headrulewidth}{0pt}
    \setlength{\headsep}{12mm}
    \usepackage{titling}
    \usepackage{booktabs}
    \usepackage{multicol}
    \setlength{\belowcaptionskip}{0pt plus 1pt minus 1pt}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(masscor)
library(xtable)
library(knitr)

 # NAWIDCC <- readRDS('../ExampleFiles/DCC_NAWI_Balanza Mettler Toledo XPE 205_B743848411 _ AF-07090_2020-07-16.rds')
 NAWIDCC <- params$NAWIDCC

```

$~$

\vspace{5ex}
\begin{center}\textsc{\huge Calibration Certificate Information}\end{center}
\vspace{8ex}\textbf{\Large `r gsub("(?<!\\w)(.)","\\U\\1", tolower(params$author), perl = TRUE)`}\newline
\textbf{`r params$address`}
\vspace{4ex}

## Certificate number: **`r NAWIDCC$add.info$CertificateNumber`**

$\hrulefill$

$~$

 \begin{tabular}{@{$\qquad\qquad$}rp{0.7\linewidth}}
 \textbf{\large Object to calibrate:}&\textbf{\large Non Automatic Weighing Instrument (NAWI)}\\[3ex]
 \textbf{Identification:}&`r NAWIDCC$balanceID`\\
 \textbf{Serial:}&`r NAWIDCC$serial`\\
 \textbf{Calibration date:}&`r NAWIDCC$date`\\
 \textbf{Calibration place:}&`r NAWIDCC$add.info$CalibrationPlace`\\[2ex]
 \textbf{Responsible person:}&`r strsplit(x = NAWIDCC$add.info$ResponsiblePerson, split = ',')[[1]][1]`\\
                     &`r ifelse(is.na(strsplit(x = NAWIDCC$add.info$ResponsiblePerson, split = ',')[[1]][2]), '', strsplit(x = NAWIDCC$add.info$ResponsiblePerson, split = ',')[[1]][2])`\\
                     &`r ifelse(is.na(strsplit(x = NAWIDCC$add.info$ResponsiblePerson, split = ',')[[1]][3]), '', strsplit(x = NAWIDCC$add.info$ResponsiblePerson, split = ',')[[1]][3])`\\[2ex]
\multicolumn{2}{@{}l}{\textit{Environmental conditions during calibration}}\\
\textbf{Ambient temperature:} & `r paste(NAWIDCC$Temp, ifelse(NAWIDCC$unitsENV[1] == 'deg.C', '$^oC$', NAWIDCC$unitsENV[1]), sep = ' ')`\\
\textbf{Barometric pressure:} & `r paste(NAWIDCC$p, NAWIDCC$unitsENV[2], sep = ' ')`\\
\textbf{Relative humidity:}   & `r paste(NAWIDCC$h, ifelse(NAWIDCC$unitsENV[3] == '%', '\\%', ''), sep = ' ')`\\
\end{tabular}

$~$

$\hrulefill$

\vspace{1ex}
## NAWI description

\begin{tabular}{@{$\qquad\qquad\qquad$}rrl}
 \textbf{ Maximum load:}&\textbf{`r max(NAWIDCC$indError[, 1])`} & `r NAWIDCC$orgdUnits`\\
 \textbf{ Minimum load:}&\textbf{`r min(NAWIDCC$indError[, 1])`} & `r NAWIDCC$orgdUnits`\\
 \textbf{ Readability:} &\textbf{`r convertMassUnitsSI(NAWIDCC$d, from = NAWIDCC$standardUnits, to = NAWIDCC$orgdUnits)`} & `r NAWIDCC$orgdUnits`\\
\end{tabular} 
   

$~$

$\hrulefill$

\begin{flushright}\texttt{masscor App Version: `r NAWIDCC$add.info$masscorAppVersion`}\end{flushright}

\clearpage

## Repeatability test results

```{r, echo = FALSE}
kable(rbind(t(apply(NAWIDCC$add.info$CompleteRepeatability, MARGIN = 2, 
                    function(x) format(x, scientific = FALSE, 
                                       nsmall = abs(floor(log10(convertMassUnitsSI(NAWIDCC$d, from = NAWIDCC$standardUnits, to = NAWIDCC$orgRepUnits[1]))))))),
            '.' = rep('', nrow(NAWIDCC$add.info$CompleteRepeatability)),
            Load = format(NAWIDCC$rep$V1, scientific = FALSE, digits = 4),
            'Standard.deviation' = signif(NAWIDCC$rep$V2, 2)),
      format = "simple", caption = paste0('Repeatability test data. Units: [', NAWIDCC$orgRepUnits[1], ']'), align = 'r',
      col.names = paste(rownames(NAWIDCC$add.info$CompleteRepeatability), '/', NAWIDCC$orgRepUnits[1], sep = ' '), booktabs = TRUE)
```

$\hrulefill$

## Excentricity test results
\begin{minipage}{.3\textwidth}
  \includegraphics[width = 3cm]{eccen.png}
\end{minipage}
\begin{minipage}{.5\textwidth}
```{r, echo = FALSE, results = "asis"}
make_outputs <- function() {
  print(kable(rbind(t(apply(NAWIDCC$add.info$CompleteRepeatability, MARGIN = 2, 
                    function(x) format(x, scientific = FALSE, 
                                       nsmall = abs(floor(log10(convertMassUnitsSI(NAWIDCC$d, from = NAWIDCC$standardUnits, to = NAWIDCC$orgRepUnits[1]))))))),
            '.' = rep('', nrow(NAWIDCC$add.info$CompleteRepeatability)),
            Load = format(NAWIDCC$rep$V1, scientific = FALSE, digits = 4),
            'Standard.deviation' = signif(NAWIDCC$rep$V2, 2)),
      format = "simple", caption = paste0('Repeatability test data. Units: [', NAWIDCC$orgRepUnits[1], ']'), align = 'r',
      col.names = paste(rownames(NAWIDCC$add.info$CompleteRepeatability), '/', NAWIDCC$orgRepUnits[1], sep = ' '), booktabs = TRUE))
  #plot(mtcars$mpg, mtcars$cyl)
  print(kable(rbind(t(apply(NAWIDCC$add.info$CompleteRepeatability, MARGIN = 2, 
                    function(x) format(x, scientific = FALSE, 
                                       nsmall = abs(floor(log10(convertMassUnitsSI(NAWIDCC$d, from = NAWIDCC$standardUnits, to = NAWIDCC$orgRepUnits[1]))))))),
            '.' = rep('', nrow(NAWIDCC$add.info$CompleteRepeatability)),
            Load = format(NAWIDCC$rep$V1, scientific = FALSE, digits = 4),
            'Standard.deviation' = signif(NAWIDCC$rep$V2, 2)),
      format = "simple", caption = paste0('Repeatability test data. Units: [', NAWIDCC$orgRepUnits[1], ']'), align = 'r',
      col.names = paste(rownames(NAWIDCC$add.info$CompleteRepeatability), '/', NAWIDCC$orgRepUnits[1], sep = ' '), booktabs = TRUE))
  }

make_outputs()

```
\end{minipage}
\end{document}


$\hrulefill$

## Indication error test
