---
params: 
  title: "Calibration Certificate Information"
  author: "Calibrating Laboratory"
  address: na
  date: '`r format(Sys.Date(), "%B %d, %Y")`'
  NAWIDCC: na
  logoBolean: na
output: 
  html_document:
  pdf_document:
      keep_tex: true
      includes:
          in_header: header.tex
title: '`r params$title`'
author: na
date: '`r params$date`'
---
<style type="text/css">
body{ /* Normal  */ font-size: 12px; }
td {  /* Table  */  font-size: 8px;}
h1.title {font-size: 24px; color: #59748f;}
h1 { /* Header 1 */ font-size: 20px; color: #59748f;}
h2 { /* Header 2 */ font-size: 17px; color: #59748f;}
h3 { /* Header 3 */ font-size: 15px; font-family: "Times New Roman", Times, serif; color: #59748f;}
code.r{ /* Code block */ font-size: 12px;}
pre { /* Code block - determines code spacing between lines */ font-size: 14px;}
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r logoHTML, include = knitr::is_html_output(), echo = FALSE}
if (params$logoBolean) {
  if (knitr::is_html_output()) {
    htmltools::img(src = knitr::image_uri(file.path("Logo.PNG")),
                   alt = '(Institution Logo)', style = 'position:absolute; top:0; right:0; padding:10px; width:40%;')
  }
}


```

# `r params$author`
### `r params$address`
|
|
## Certificate number: `r params$NAWIDCC$add.info$CertificateNumber`

---

## Object: Non Automatic Weighing Instrument (NAWI)


directory: `r print(getwd())`
```{r}
print(getwd())
print(params$logoBolean)
class(params$NAWIDCC)
```